Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-12 write-ups/PLDI/paper.tex
More feedback from Paul.

As with a regular OpenCL kernel (see \mysec\ref{sec:opencl}), a
cooperative kernel is launched by the host application.  The host
application passes parameters to the kernel and specifies a desired
number of workgroups, each consisting of a specified number of
threads.  The parameters to a cooperative kernel are \emph{immutable}, as if
they were qualified with the \texttt{const} keyword (though pointer
parameters can refer to mutable data).

@@

The workgroups executing the kernel are called \emph{active
  workgroups}, and $M$ denotes the number of active workgroups.
Initially, the number of active workgroups $M$ is initialised to some
integer between $1$ and $N$.  The initial active workgroups have
consecutive workgroup ids in the range $[0, M-1]$.

>>>>

As with a regular OpenCL kernel (see \mysec\ref{sec:opencl}), a
cooperative kernel is launched by the host application.  The host
application passes parameters to the kernel and specifies a desired
number of workgroups, each consisting of a specified number of
threads.  Unlike in a regular kernel, the parameters to a cooperative kernel are \emph{immutable}, as if
they were qualified with the \texttt{const} keyword (though pointer
parameters can refer to mutable data).

@@

The workgroups executing the kernel are called \emph{active
  workgroups}, and $M$ denotes the number of active workgroups.
Initially, the number of active workgroups $M$ is initialised to some
integer between $1$ and $N$---to ensure that at least one workgroup is scheduled, the scheduler will postpone execution of the kernel until a some compute unit becomes available.  The initial active workgroups have
consecutive workgroup ids in the range $[0, M-1]$.
